Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-08-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
slightly rewrite flight campaign sentence
delete redundant with

The airborne hyperspectral data was acquired during two flight campaigns on September 28th and October 5th 2016, both around noon.
The images were taken by an AISAEAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) were conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in \autoref{tab:hyperparameter_metadata}.

@@

High-dimensional, feature-rich datasets come with with several challenges for both model fitting and evaluation.

>>>>

The airborne hyperspectral data was acquired during two flight campaigns which took at noon on September 28th and October 5th 2016.
The images were taken by an AISAEAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) were conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in \autoref{tab:hyperparameter_metadata}.

@@

High-dimensional, feature-rich datasets come with several challenges for both model fitting and evaluation.
